%Due to our investigation with the summation circuit it is likely that the higher the frequency the less accurate a summed signal will be. It is recommended that a low frequency is set, we would recommend 5Hz based off our initial tests.
The purpose of this lab was to investigate the analogue computer through six different circuits.The first circuit was a summing circuit, we had two input voltages and the output would be the sum of the two circuits. When the data was analyzed we found that it fit well with the theory presented. Although due to our investigation with the summation circuit it is likely that the higher the frequency the less accurate a summed signal will be. It is recommended that a low frequency is set, we would recommend 5Hz based off our initial tests. The next circuit that we we looked at was the differentiating circuit, for this we had to filter the results and once we had done so we saw that the the results fit the theory. We then looked at the integrating circuit, here we found that the output voltage and the calculated voltage were not the same and we attribute it to the slew rate of the op-amp. The next circuit dealt with exponential functions and on this on one we determined that were we found that for some of the data that we obtained the results did not fare well with the theory. This however is not unexpected as we are allowing very little of the original signal to be fed back into the input of the circuit. Also we were unable to fully explain the unexpected signal that we obtained for Figure 28a, and thing that it may be due to the capacitor based off of the signals curvature. The data obtained for the damped harmonic motion did not allow us to properly gain insight into this circuit. The plots that we obtained did not follow the expected plots for damped harmonic motion. We were able to determine whand finallycause this but are unable to fully explain the discrepancy.   we looked at forat did not ced damped harmonic motion were we found the $Q_{actual} = 1.838$ while the $Q{theory} = 4.01$.